Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2018-09-16 paper/drafts/draft_final.tex
Firdya night data. I dont wanna look at a computer anymore
bara look at IEEE_VERSION

@@

	\subsection{2.3}
	\subsection{2.4}
	\section{3}
	\subsection{Thrust stand}
	%THE THRUST STAND
	In our setup we used a thrust stand obtained from RCBenchmark, specifically the RCBenchmark Thrust stand and Dynamometer Series 1580 \cite{rcb} as our testbed. The measurements from the thrust stand will be our "ground truth". This thrust stand incorporates a micro-controller board along with three, three-axis strain guage to measure the forces and the torque derived by the propeller. The board also collects data on the voltage, current and the signal to the ESC's which allows us to measure the power draw of the motor, and the RPM of the motor. Along with this there is an associated GUI which allows us to control the board and collect and visualize the data. The testbed collects data at a very high rate of close to 1kHz but then averages the data to eliminate outliers, so the data rate is 40Hz. This is more than adequate for the purposes of modeling the thrust response of the propeller to various stimuli. 
	\subsection{Wind Sensor Intro}
	The wind sensor we have chosen to use is the "Modern Device- Wind Sensor Rev. P" \cite{md}. This device is a hot wire anemometer that is designed to measure wind from any direction. Hot wire anemometers work by passing a constant current through a thin wire which heats up due to the current. As the wind flows past the wire, the wire will be cooled down rapidly, resulting in a change in the measured voltage, which is the value that we observe \cite{hot_wire}. This system allows us to measure the wind speed that is resultant of the propeller. 
	\subsection{Wind Sensor Proof}
	To understand the limitations of the wind sensor, we performed a series of tests to characterize the sensor. The first of which was to determine under which orientation the sensor observed the highest range of wind speeds. As seen in \ref{orient_test}, the orientation of placing the wind sensor normal to the direction of wind flow allowed for the highest range of measurement. Next we performed a test to determine the feasible range of measurement. This was done by exposing the wind sensor to a step-signal test and a pulse signal test ranging from the minimal PWM value to approximately $50\%$ of the motor's max value, the results of which are in \ref{min_max}. The PWM values in this case are based around the Simulink-Arduino Library PWM module.  This resulted in a working range from $PWM = 44$ to $PWM = 60$. While there is possibility for the wind sensor to measure higher wind speeds, there is a significant amount of noise even with the addition of a low-pass filter, hence we decided to limit the max speed of our experiment. 
	Another factor that we deem is important to characterize is the speed of response to change of wind speed. We measured this by running the propeller at various different speeds, while tracking the thrust output on the testbed as our base measurement of response time and then comparing the response time to see the lag in response time. By doing this we found that there was a negligible lag time of less than $10 ms$, which is our resolution for each measurement.
	Lastly we measured the location of the wind sensor in relation to the propellers. To do so we measured a semi-circle area behind the propeller to deem the location of highest wind sensitivity. Resulting in a map as seen in figure \ref{area}. 
	By characterizing the wind sensor, we can ensure that it is in the optimal configuration for us to collect data.
	\section{Results}
	\subsection{Experimental Setup- How we set up the kalman/Algorithm}

	We developed a control architecture as pictured in fig \ref{block_diagram} where there are two sources of measurement for the thrust value. the primary value is from the wind sensor which is measured through an Arduino. The voltage value that the arduino measures is then converted to a thrust value through the power function
	\begin{equation}
	Thrust = 4.701 * 10^{15} * V_w^{6.146} + 0.0731
	\label{wind_power}
	\end{equation}
	The secondary measurement of thrust is a polynomial function that converts the output PWM value that is used to control the propeller. \newline
	\begin{eqnarray}
	Thrust = 1.957*10^{-5}*PWM^4 \\
	- 7.476*10^{-4}*PWM^3 \nonumber\\ 
	+ 1.272*10^{-2}*PWM^2 \nonumber\\
	+ .01092*PWM - .01842 \nonumber
	\label{pwm_poly}
	\end{eqnarray}
	These values are then passed through a Kalman Filter weighted towards the wind sensor. This method allows for the system to accurately determine the thrust value output while reducing noise due to the nature of the wind. Next this value is passed to a PI controller which generates the appropriate response for the error between desired and measured. 
	\subsection{The tests}
	To ensure the viability of our algorithm and if it would respond to external stimuli the way we expected, we performed several tests that caused significant errors in the propeller's response. The first test that we ran was to measure the response of the kalman filter and ensure that our thrust calculation was accurate in relation to the testbed recorded thrust. As seen in fig \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely. This result gives us the confidence to setup the PI based on the kalman filter's value. 
	To ensure the functionality of the controller we set up several faults and disturbances to test the response of the system. The first step was to create an external disturbance by placing another propeller and blowing wind perpendicular to the axis of the main propeller. This would be akin to horizontal crosswind flow across the propeller.
	\begin{figure}
		\label{content...}
	\end{figure}
	 Based on the results of fig \ref{wind_disturb}, the control algorithm can determine the appropriate correction for such a disturbance through
	\begin{figure}
		content...
	\end{figure}
	\subsection{Shortcomings and limitations}
	As mentioned previously, having a closed loop system allows for a more robust and agile system which allows for better flight performance. Some of the application for this level of performance include a better landing algorithm, proximity detection of other MAV's, more sophisticated hovering control, fault detection, and fault tolerance. These areas would all benefit by having a physical measurement of the thrust rather than an estimation.

@@

	\subsection{}
	\subsection{5.4}
		\begin{figure}[b]
		\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
		\caption{Block Diagram}
		\label{block_diagram}
	\end{figure}
	\begin{thebibliography}{99}
		\bibitem{mahoney1} Mahoney 2012
		\bibitem{rcb} https://www.rcbenchmark.com/dynamometer-series-1580/
		\bibitem{md} https://moderndevice.com/product/wind-sensor-rev-p/
		\bibitem{hot_wire} Extended Applications of the Hot‐Wire Anemometer, Stanley Corrsin,Review of Scientific Instruments 1947 18:7, 469-471 
		\bibitem{awan} A. U. Awan, J. Park and H. J. Kim, "Thrust estimation of quadrotor UAV using adaptive observer," 2011 11th International Conference on Control, Automation and Systems, Gyeonggi-do, 2011, pp. 131-136.
		\bibitem{sydney} N. Sydney, B. Smyth and D. A. Paley, "Dynamic control of autonomous quadrotor flight in an estimated wind field," 52nd IEEE Conference on Decision and Control, Florence, 2013, pp. 3609-3616.
		doi: 10.1109/CDC.2013.6760438

>>>>

	\IEEEauthorblockA{\textit{dept. namefdsfsdf of organization (of Aff.)} \\

@@

	Adaptive Fuzzy Kalman Filter 
	Accurate a priori information of the measurement and process noise statistical matrices of the state estimator is needed to avoid the divergence of the filter [3], [4]. To resolve the problem of having imperfect a priori information, adapting R and/or Q matrices was introduced using several adaptive estimation techniques [5]–[7]. Among these, the Innovative-based Adaptive Estimation (IAE) and Multiple Model Adaptive Estimation (MMAE) are commonly utilized to adapt the Kalman filter. Incorporating the rules of fuzzy logic to adjust the variances of these matrices has been studied in several research works. The Adaptive Fuzzy Kalman Filter q (AFKF) has been designed to improve the performance of the conventional filter in rejecting the measurement noise and estimating the navigational states accurately [8], [9]. 
	The recurrent adjustment process of the variances of the statistical matrices Rk is designed based on an IAE approach. This approach is based on a covariance-matching algorithm which examines the degree of the mismatch DoM between the actual covariance $v_{K+1}$ of the residual with its theoretical value $S_{K+1}$. 
	DoM = S_{k+1} - C_{k+1}
	\label{dom}
	After calculating DoM, a Fuzzy Inference System (FIS) has been tuned to compute the adjustment of the measurement noise matrix $R_{k+1}$ and update the matrix at each cycle of state estimation.
	R_{k+1} = R_k +\delta R_{K+1}
	\label{rk1}

	\section{3}
	\subsection{Thrust stand}
	%THE THRUST STAND
	In our setup we used a thrust stand obtained from RCBenchmark, specifically the RCBenchmark Thrust stand and Dynamometer Series 1580 \cite{rcb} as our testbed. The measurements from the thrust stand will be our "ground truth". This thrust stand incorporates a micro-controller board along with three, three-axis strain guage to measure the forces and the torque derived by the propeller. The board also collects data on the voltage, current and the signal to the ESC's which allows us to measure the power draw of the motor, and the RPM of the motor. Along with this there is an associated GUI which allows us to control the board and collect and visualize the data. The testbed collects data at a very high rate of close to 1kHz but then averages the data to eliminate outliers, so the data rate is 40Hz. This is more than adequate for the purposes of modeling the thrust response of the propeller to various stimuli. 
	\subsection{Wind Sensor Intro}
	The wind sensor we have chosen to use is the "Modern Device- Wind Sensor Rev. P" \cite{md}. This device is a hot wire anemometer that is designed to measure wind from any direction. Hot wire anemometers work by passing a constant current through a thin wire which heats up due to the current. As the wind flows past the wire, the wire will be cooled down rapidly, resulting in a change in the measured voltage, which is the value that we observe \cite{hot_wire}. This system allows us to measure the wind speed that is resultant of the propeller. 
	\subsection{Wind Sensor Proof}
	To understand the limitations of the wind sensor, we performed a series of tests to characterize the sensor. The first of which was to determine under which orientation the sensor observed the highest range of wind speeds. As seen in \ref{orient_test}, the orientation of placing the wind sensor normal to the direction of wind flow allowed for the highest range of measurement. Next we performed a test to determine the feasible range of measurement. This was done by exposing the wind sensor to a step-signal test and a pulse signal test ranging from the minimal PWM value to approximately $50\%$ of the motor's max value, the results of which are in \ref{min_max}. The PWM values in this case are based around the Simulink-Arduino Library PWM module.  This resulted in a working range from $PWM = 44$ to $PWM = 60$. While there is possibility for the wind sensor to measure higher wind speeds, there is a significant amount of noise even with the addition of a low-pass filter, hence we decided to limit the max speed of our experiment. 
	Another factor that we deem is important to characterize is the speed of response to change of wind speed. We measured this by running the propeller at various different speeds, while tracking the thrust output on the testbed as our base measurement of response time and then comparing the response time to see the lag in response time. By doing this we found that there was a negligible lag time of less than $10 ms$, which is our resolution for each measurement.
	Lastly we measured the location of the wind sensor in relation to the propellers. To do so we measured a semi-circle area behind the propeller to deem the location of highest wind sensitivity. Resulting in a map as seen in figure \ref{area}. 
	By characterizing the wind sensor, we can ensure that it is in the optimal configuration for us to collect data.
	\section{Results}
	\subsection{Experimental Setup- How we set up the kalman/Algorithm}

	We developed a control architecture as pictured in fig \ref{block_diagram} where there are two sources of measurement for the thrust value. the primary value is from the wind sensor which is measured through an Arduino. The voltage value that the arduino measures is then converted to a thrust value through the power function
	\begin{equation}
	Thrust = 4.701 * 10^{15} * V_w^{6.146} + 0.0731
	\label{wind_power}
	\end{equation}
	The secondary measurement of thrust is a polynomial function that converts the output PWM value that is used to control the propeller. \newline
	\begin{eqnarray}
	Thrust = 1.957*10^{-5}*PWM^4 \\
	- 7.476*10^{-4}*PWM^3 \nonumber\\ 
	+ 1.272*10^{-2}*PWM^2 \nonumber\\
	+ .01092*PWM - .01842 \nonumber
	\label{pwm_poly}
	\end{eqnarray}
	These values are then passed through a Kalman Filter weighted towards the wind sensor. This method allows for the system to accurately determine the thrust value output while reducing noise due to the nature of the wind. Next this value is passed to a PI controller which generates the appropriate response for the error between desired and measured. 
	\subsection{The tests}
	Figures \ref{akf1},\ref{akf2} demonstrate the thrust estimation using the conventional and the adaptive fuzzy state estimation techniques. As can be seen, the proposed AFKF has exhibited better performance in terms of rejecting the noise associated with the measurement compared to the classical KF. Figures \ref{akf1},\ref{akf2} presents the estimation errors of the position states. The AFKF shows lower magnitudes of estimation error compared to these of the KF.

	To ensure the viability of our algorithm and if it would respond to external stimuli the way we expected, we performed several tests that caused significant errors in the propeller's response. The first test that we ran was to measure the response of the kalman filter and ensure that our thrust calculation was accurate in relation to the testbed recorded thrust. As seen in fig \ref{kalman} the kalman filter, while noisy due to the wind variations in the wind sensor data, follows the thrust value from the testbed closely. This result gives us the confidence to setup the PI based on the kalman filter's value. 
	To ensure the functionality of the controller we set up several faults and disturbances to test the response of the system. The first step was to create an external disturbance by placing another propeller and blowing wind perpendicular to the axis of the main propeller. This would be akin to horizontal crosswind flow across the propeller.
	\begin{figure}
		\label{content...}
	\end{figure}
	 Based on the results of fig \ref{wind_disturb}, the control algorithm can determine the appropriate correction for such a disturbance through
	\begin{figure}
		content...
	\end{figure}
	\subsection{Shortcomings and limitations}
	As mentioned previously, having a closed loop system allows for a more robust and agile system which allows for better flight performance. Some of the application for this level of performance include a better landing algorithm, proximity detection of other MAV's, more sophisticated hovering control, fault detection, and fault tolerance. These areas would all benefit by having a physical measurement of the thrust rather than an estimation.

@@

	\subsection{}
	\subsection{5.4}
		\begin{figure}[b]
		\includegraphics[width=\textwidth / 2]{images/block_diagram.png}
		\caption{Block Diagram}
		\label{block_diagram}
	\end{figure}
	\begin{thebibliography}{99}
		\bibitem{mahoney1} Mahoney 2012
		\bibitem{rcb} https://www.rcbenchmark.com/dynamometer-series-1580/
		\bibitem{md} https://moderndevice.com/product/wind-sensor-rev-p/
		\bibitem{hot_wire} Extended Applications of the Hot‐Wire Anemometer, Stanley Corrsin,Review of Scientific Instruments 1947 18:7, 469-471 
		\bibitem{awan} A. U. Awan, J. Park and H. J. Kim, "Thrust estimation of quadrotor UAV using adaptive observer," 2011 11th International Conference on Control, Automation and Systems, Gyeonggi-do, 2011, pp. 131-136.
		\bibitem{sydney} N. Sydney, B. Smyth and D. A. Paley, "Dynamic control of autonomous quadrotor flight in an estimated wind field," 52nd IEEE Conference on Decision and Control, Florence, 2013, pp. 3609-3616.
